\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
siamese question

\todo[inline]{Looking at the code, I wonder if what is implemented is
  actually a Siamese ANN; it does not look as if the weights are
  shared between the two networks, so looks more like a twin or
  half-twin network?}

>>>>

\todo[inline]{Looking at the code, I wonder if what is implemented is
  actually a Siamese ANN; it does not look as if the weights are
  shared between the two networks, so looks more like a twin or
  half-twin network? Siamese would be sim(f(e1),f(e2)) but the
  implementation seems to be sim(f(e1), g(e2)).}
